|

### 2023-01-10 paper.Rmd
Tue Jan 10 11:00:11 CET 2023: update-remote.sh

```{python, load_MWU, include=FALSE}
from json import load

S = load(open("./data/airfoil_FullRun_30gens/MWU-BestFitnessByGen.json", "r", encoding="utf-8"))
statistic_mwu_fitness = S["statistic"]
pval_mwu_fitness = round(S["p-value"], 4)
print(pval_mwu_fitness)
```

The result of the MWU test is `r py$pval_mwu_fitness`

@@

>>>>

@@

<!-- Overview Real World SymReg  -->

To gather more confidence in the previous results, the pre-training strategy for DAE-GP was tested for various real world symbolic regression problems taken from @machine_learning_repo. Are brief summary of the benchmark problems is given in table X

```{r full_run_realWorldSymReg_problems, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/full_run_realWorldSymReg_problems.csv"),
  caption="Overview - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
Table X summarizes the median best fitness achieved after running each algorithm for 30 runs using a population size of 500 individuals.^[P-Values are marked with asteriks (1,2,3) for ($\alpha$) (0.1, 0.05 and 0.01)].

``` {bash recreate_csv_file_benchmarkRWSymReg, include=FALSE}
/Users/rmn/miniconda3/envs/dataScience/bin/python /Users/rmn/github/master_thesis/data/summarize_finalFitness.py
```

```{r full_run_realWorldSymReg_performance, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv", sep=","),
  caption="Performance - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```
